\textmd{\hmwkClass:\ \hmwkTitle}\\ \normalsize{\hmwkClassInstructor}\\ \small{Due\ on\ \hmwkDueDate}

### 2017-05-08 paper/main.tex
Added reason for objects updating itself

what we did, how we did it, why we did it

@@

\subsection{Updating Physical Objects}
There are mainly two ways we could update object positions: 1) The evolver can take in a list of forces and objects and apply forces as appropriate 2) Each object can be registered with a set of forces applicable to them and the evolver can call each object to evolve themselves.

We chose the second model where each object does its own updating because [blank].

>>>>

@@

\subsection{Updating Physical Objects}
There are mainly two ways positions of physical objects could be updated: 1) The evolver can take in a list of forces and objects and apply forces as appropriate 2) Each object can be registered with a set of forces applicable to it and the evolver can call each object to evolve itself.

Our system adopted the second model where each object updates itself. This model makes it easier to handle different types of forces exerted on specific types of object. Moreover, in the second model, the engine does not need to be notified and updated everytime a new object is added. Instead, update or addition of new \texttt{interaction}s is taken care of at the object level when it is added.
